\textbf{Supplementary Information}

### 2020-03-04 submission/manuscript.tex
Discussion progress.

The majority of studies describing macrophyte epiphytic communities did
not encompass seasonal changes (Crump and Koch, 2008; Lachnit \emph{et
al.}, 2009; Burke \emph{et al.}, 2011b; Roth-Schulze \emph{et al.},
2016; Ugarelli \emph{et al.}, 2019). In addition, if seasonal changes
were taken into account low temporal frequency and/or methodologies that
do not allow for high taxonomic resolution were used (Tujula \emph{et
al.}, 2010; Lachnit \emph{et al.}, 2011; Miranda \emph{et al.}, 2013).
In the present study we describe the seasonal dynamics of bacterial and
archaeal communities on the surfaces of the seagrass \emph{Cymodocea
nodosa} and siphonous macroalgae \emph{Caulerpa cylindracea} determined
on a mostly monthly scale. Bacterial and archaeal epiphytes were sampled
in a meadow of \emph{Cymodocea nodosa} invaded by the invasive
\emph{Caulerpa cylindracea} and in a locality of only \emph{Caulerpa
cylindracea} located in the proximity of the meadow. In addition, for
comparison, the community of the surrounding seawater was characterized.

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

To determine the proportion of shared archaeal and bacterial OTUs and
communities sampled in different environments the Jaccard's Similarity
Coefficient on presence-absence data and Bray-Curtis Similarity
Coefficient were, respectively, calculated. Coefficients were determined
after normalization through rarefaction and binning of samples from a
particular environment. The highest proportion of shared OTUs and
community was found between invaded and noninvaded \emph{Caulerpa
cylindracea} (Jaccard, 0.35; Bray-Curtis, 0.77), while lower shared
values were calculated between seawater and epiphytic communities
(\autoref{matrix}). Shared proportion between \emph{Cymodocea nodosa}
and \emph{Caulerpa cylindracea} were approximately in the middle between
these two extremes. To assess seasonal changes in the proportion of
shared OTUs and communities the Jaccard's and Bray-Curtis Similarity
Coefficients were calculated between consecutive sampling points
(\autoref{shared}). Both coefficients showed similar trends. Temporal
proportional changes were more pronounced for seawater in comparison to
\emph{Cymodocea nodosa} and especially \emph{Caulerpa cylindracea}
associated communities (\autoref{shared}). To further disentangle the
environmental and seasonal community dissimilarity a Principal
Coordinates Analysis (PCoA) based on Bray-Curtis distances and OTU
abundances was applied. It showed a clear separation between planktonic
and surface associated communities (\autoref{pcoa}). In addition, a
separation of epiphytic bacterial and archaeal communities based on host
species was determined. This separation was further supported by ANOSIM
(R = 0.96, \emph{p} \textless{} 0.001). Seasonal changes of seawater
communities indicated a separation between Spring, Summer and
Autumn/Winter samples (ANOSIM, R = 0.64, \emph{p} \textless{} 0.001).
Epiphytic microbial communities associated with \emph{Cymodocea nodosa}
showed a similar pattern (ANOSIM, R = 0.56, \emph{p} \textless{} 0.01),
while communities from the surfaces of \emph{Caulerpa cylindracea}
indicated a non so strongly supported, as in previous cases, separation
between Summer and Autumn/Winter/Spring samples (ANOSIM, R = 0.31,
\emph{p} \textless{} 0.05) (\autoref{pcoa}).

The taxonomic composition of both, macrophyte associated and seawater
communities, was dominated by \emph{Bacteria} (99.1 ± 2.1 \si{\percent})
over \emph{Archaea} (0.9 ± 2.1 \si{\percent}) (\autoref{community}).
Higher relative abundances of chloroplast related sequences were only
observed in surface associated communities, with higher values in
Autumn/Winter (37.2 ± 11.2 \si{\percent}) in comparison to Spring/Summer
(20.9 ± 9.7 \si{\percent}) (\autoref{supp-chloroplast}). Generally, at
higher taxonomic ranks (phylum-class) epiphytic and seawater microbial
communities were composed of similar bacterial taxa. Seawater
communities were mainly comprised of \emph{Actinobacteriota},
\emph{Bacteroidota}, \emph{Cyanobacteria}, \emph{Alphaproteobacteria},
\emph{Gammaproteobacteria} and \emph{Verrucomicrobiota}. Communities
associated with \emph{Cymodocea nodosa} were consisted of same groups
with the addition of \emph{Planctomycetota} whose contribution was
higher in summer 2018. In addition, communities from invaded and
noninvaded \emph{Caulerpa cylindracea} were similar and characterized by
same groups as seawater and \emph{Cymodocea nodosa} communities with the
addition of \emph{Desulfobacterota} (\autoref{community}). Larger
differences between environments and host species could be observed at
lower taxonomic ranks (\autoref{cyano} -- \ref{desulfo}).

Surfaces of marine macrophytes are harboring biofilms consisted of
diverse microbial taxa (Egan \emph{et al.}, 2013; Tarquinio \emph{et
al.}, 2019). No standard protocol has been developed to study these
macophyte associated microbes (Ugarelli \emph{et al.}, 2019). Different
procedures of microbial cells removal from host surfaces were described,
such as host tissue shaking (Nõges \emph{et al.}, 2010), scraping (Uku
\emph{et al.}, 2007) and ultrasonication (Cai \emph{et al.}, 2014). All
these methods showed different removal efficiencies and none was
enabling a complete removal of attached microbial cells. In the present
study, we applied an earlier developed removal protocol (Korlević
\emph{et al.}, submitted), based on a previous idea of direct cellular
lysis (Burke \emph{et al.}, 2009), to ensure an almost complete cell
detachment. The application of a direct lysis procedure coupled with a
high frequency sampling protocol and Illumina high resolution amplicon
sequencing has enabled us to make a detailed description of bacterial
and archaeal communities associated with the surfaces of two marine
macrophytes, \emph{Cymodocea nodosa} and \emph{Caulerpa cylindracea}.

Observed highest richness values for \emph{Caulerpa cylindracea}
(invaded and noninvaded), middle for \emph{Cymodocea nodosa} and lowest
for seawater derived communities. Higher values for surface associated
communities in comparison to seawater were described earlier for
seagrasses (Ugarelli \emph{et al.}, 2019) and could be attributed to a
larger set of inhabitable microniches existing on macrophyte surfaces.
In addition, highest values observed for \emph{Caulerpa cylindracea} are
probably a consequence of sediment derived OTUs that were present only
in \emph{Caulerpa cylindracea} communities. \emph{Caulerpa cylindracea}
stolon is attached to surface sediment with rhizoids, so the stolon and
rhizoids are in a direct contact with the sediment surface. Part of the
surface attached \emph{Caulerpa cylnidracea} community is therefore
comprised of sediment derived cells that could cause the observed
increase in richness. In addition, seasonal richness differences
observed for surface attached communities showed slightly higher values
in spring and summer could be explained by a higher macrophyte growth in
these seasons (M. Najdek, personal communication; Zavodnik \emph{et
al.}, 1998; Ruitton \emph{et al.}, 2005). During active periods
macrophytes exhibit a more dynamic chemical interaction with the surface
community causing an extension of the microniche number.

@@

@@

@@

@@

@@

@@

>>>>

The majority of studies describing macrophyte epiphytic communities did
not encompass seasonal changes (Crump and Koch, 2008; Lachnit \emph{et
al.}, 2009; Burke \emph{et al.}, 2011b; Roth-Schulze \emph{et al.},
2016; Ugarelli \emph{et al.}, 2019). In addition, if seasonal changes
were taken into account low temporal frequency and/or methodologies that
do not allow for high taxonomic resolution were used (Tujula \emph{et
al.}, 2010; Lachnit \emph{et al.}, 2011; Miranda \emph{et al.}, 2013;
Michelou \emph{et al.}, 2013). In the present study we describe the
seasonal dynamics of bacterial and archaeal communities on the surfaces
of the seagrass \emph{Cymodocea nodosa} and siphonous macroalgae
\emph{Caulerpa cylindracea} determined on a mostly monthly scale.
Bacterial and archaeal epiphytes were sampled in a meadow of
\emph{Cymodocea nodosa} invaded by the invasive \emph{Caulerpa
cylindracea} and in a locality of only \emph{Caulerpa cylindracea}
located in the proximity of the meadow. In addition, for comparison, the
community of the surrounding seawater was characterized.

@@

To determine the proportion of shared archaeal and bacterial OTUs and
communities sampled in different environments the Jaccard's Similarity
Coefficient on presence-absence data and Bray-Curtis Similarity
Coefficient were, respectively, calculated. Coefficients were determined
after normalization through rarefaction and binning of samples from a
particular environment. The highest proportion of shared OTUs and
community was found between invaded and noninvaded \emph{Caulerpa
cylindracea} (Jaccard, 0.35; Bray-Curtis, 0.77), while lower shared
values were calculated between seawater and epiphytic communities
(\autoref{matrix}). Shared proportion between \emph{Cymodocea nodosa}
and \emph{Caulerpa cylindracea} were approximately in the middle between
these two extremes. To assess seasonal changes in the proportion of
shared OTUs and communities the Jaccard's and Bray-Curtis Similarity
Coefficients were calculated between consecutive sampling points
(\autoref{shared}). Both coefficients showed similar trends. Temporal
proportional changes were more pronounced for seawater in comparison to
\emph{Cymodocea nodosa} and especially \emph{Caulerpa cylindracea}
associated communities (\autoref{shared}). In addition, only 0.4 -- 1.0
\si{\percent} of OTUs from each surface associated community were found
at every time point. These OTUs made also a high proportion of total
sequences (39.1 -- 51.3 \si{\percent}). To further disentangle the
environmental and seasonal community dissimilarity a Principal
Coordinates Analysis (PCoA) based on Bray-Curtis distances and OTU
abundances was applied. It showed a clear separation between planktonic
and surface associated communities (\autoref{pcoa}). In addition, a
separation of epiphytic bacterial and archaeal communities based on host
species was determined. This separation was further supported by ANOSIM
(R = 0.96, \emph{p} \textless{} 0.001). Seasonal changes of seawater
communities indicated a separation between Spring, Summer and
Autumn/Winter samples (ANOSIM, R = 0.64, \emph{p} \textless{} 0.001).
Epiphytic microbial communities associated with \emph{Cymodocea nodosa}
showed a similar pattern (ANOSIM, R = 0.56, \emph{p} \textless{} 0.01),
while communities from the surfaces of \emph{Caulerpa cylindracea}
indicated a non so strongly supported, as in previous cases, separation
between Summer and Autumn/Winter/Spring samples (ANOSIM, R = 0.31,
\emph{p} \textless{} 0.05) (\autoref{pcoa}).

The taxonomic composition of both, macrophyte associated and seawater
communities, was dominated by bacterial (99.1 ± 2.1 \si{\percent}) over
archaeal sequences (0.9 ± 2.1 \si{\percent}) (\autoref{community}).
Higher relative abundances of chloroplast related sequences were only
observed in surface associated communities, with higher values in
Autumn/Winter (37.2 ± 11.2 \si{\percent}) in comparison to Spring/Summer
(20.9 ± 9.7 \si{\percent}) (\autoref{supp-chloroplast}). Generally, at
higher taxonomic ranks (phylum-class) epiphytic and seawater microbial
communities were composed of similar bacterial taxa. Seawater
communities were mainly comprised of \emph{Actinobacteriota},
\emph{Bacteroidota}, \emph{Cyanobacteria}, \emph{Alphaproteobacteria},
\emph{Gammaproteobacteria} and \emph{Verrucomicrobiota}. Communities
associated with \emph{Cymodocea nodosa} were consisted of same groups
with the addition of \emph{Planctomycetota} whose contribution was
higher in summer 2018. In addition, communities from invaded and
noninvaded \emph{Caulerpa cylindracea} were similar and characterized by
same groups as seawater and \emph{Cymodocea nodosa} communities with the
addition of \emph{Desulfobacterota} (\autoref{community}). Larger
differences between environments and host species could be observed at
lower taxonomic ranks (\autoref{cyano} -- \ref{desulfo}).

Surfaces of marine macrophytes are harboring biofilms consisted of
diverse microbial taxa (Egan \emph{et al.}, 2013; Tarquinio \emph{et
al.}, 2019). No standard protocol has been developed to study these
macophyte associated microbes (Ugarelli \emph{et al.}, 2019). Different
procedures of microbial cells removal from host surfaces were described,
such as host tissue shaking (Nõges \emph{et al.}, 2010), scraping (Uku
\emph{et al.}, 2007) and ultrasonication (Cai \emph{et al.}, 2014). All
these methods showed different removal efficiencies but none was
enabling a complete removal of attached microbial cells. In the present
study, we applied an earlier developed removal protocol (Korlević
\emph{et al.}, submitted), based on a previous idea of direct cellular
lysis (Burke \emph{et al.}, 2009), to ensure an almost complete cell
detachment. The application of a direct lysis procedure coupled with a
high frequency sampling protocol and Illumina high resolution amplicon
sequencing has enabled us to make a detailed description of bacterial
and archaeal communities associated with the surfaces of two marine
macrophytes, \emph{Cymodocea nodosa} and \emph{Caulerpa cylindracea}.

In the present study, highest richness values were observed for
\emph{Caulerpa cylindracea} (invaded and noninvaded), middle for
\emph{Cymodocea nodosa} and lowest for seawater derived communities.
Higher values for seagrass associated communities in comparison to
seawater were described earlier and could be attributed to a larger set
of inhabitable microniches existing on macrophyte surfaces (Ugarelli
\emph{et al.}, 2019). In addition, highest values observed for
\emph{Caulerpa cylindracea} are probably a consequence of part of
epiphytic OTUs that are in contact with the sediment. \emph{Caulerpa
cylindracea} stolon is attached to the sediment surface with rhizoids,
so the stolon and rhizoids are in a direct contact with the sediment.
Part of the surface attached \emph{Caulerpa cylnidracea} community is
therefore comprised of OTUs that are in contact with a different
environment and that could cause the observed increase in richness. In
addition, seasonal richness differences observed for surface attached
communities showed slightly higher values in spring and summer. This
pattern could be explained by a higher macrophyte growth in these
seasons (M. Najdek, personal communication; Zavodnik \emph{et al.},
1998; Ruitton \emph{et al.}, 2005). During active periods macrophytes
exhibit a more dynamic chemical interaction with the surface community
probably causing an increase in the number of inhabitable microniches
(Borges and Champenois, 2015; Rickert \emph{et al.}, 2016).

Since the colonization of macrophyte surfaces is performed from a pool
of seawater prokaryotic cells it is interesting to see to which extent
do these two communities differ. We observed a strong differentiation
between the surface attached and seawater communities at the level of
OTUs that is in agreement with most published studies (Burke \emph{et
al.}, 2011b; Michelou \emph{et al.}, 2013; Roth-Schulze \emph{et al.},
2016; Ugarelli \emph{et al.}, 2019). These data indicate that marine
macrophytes are selecting, from a pool of seawater microbial taxa, the
one that can colonize and proliferate on their surfaces (Salaün \emph{et
al.}, 2012; Michelou \emph{et al.}, 2013). In contrast to these findings
Fahimipour \emph{et al.} (2017) found, in a global study of
\emph{Zostera marina}, similarities between leaves and seawater samples.
Discrepancies between our data and this study could be explained by
differences in studied seagrass species, methodological variations or
biogeographic trends as Fahimipour \emph{et al.} (2017) were analyzing
samples from different locations throughout the northern hemisphere. It
is possible that ambient seawater and leaves communities from the same
location are differing but are still more similar to each other when
compared to other sampling locations. Indeed, it was found that
prokaryotic communities vary substantially between different sampling
sites (Bengtsson \emph{et al.}, 2017). When the taxonomic composition at
high ranks was analyzed no such strong differentiation was noticed.
Phyla and classes such as: \emph{Actinobacteriota}, \emph{Bacteroidota},
\emph{Cyanobacteria}, \emph{Alphaproteobacteria},
\emph{Gammaproteobacteria} and \emph{Verrucomicrobiota}, were described
that is in agreement with previously reported data (Burke \emph{et al.},
2011b; Egan \emph{et al.}, 2013; Michelou \emph{et al.}, 2013). In
contrast, when low taxonomic ranks were analyzed (i.g. family and genus)
a strong differentiation was observed. A similar differentiation at
lower taxonomic ranks was described for other species of macrophytes
(Egan \emph{et al.}, 2013; Michelou \emph{et al.}, 2013; Ugarelli
\emph{et al.}, 2019).

Beside differences between seawater and surface associated communities,
there were discussions if the prokaryotic epiphytic community is
host-specific or there are generalists taxa characteristic to all or
many macrophytes (Egan \emph{et al.}, 2013). Similarly to previously
described differences between seawater and surface attached communities,
at high taxonomic ranks no strong differentiation between communities
associated with different host was observed. The only high rank phylum
that was differing between \emph{Cymodocea nodosa} ans \emph{Caulerpa
cylindracea} was \emph{Desulfobacterota}, whose sequences were more
abundant in the \emph{Caulerpa cylindracea} associated community. As
already mentioned, the rhizoids and part of the stolon are in contact
with the sediment, so \emph{Desulfobacterota} are probably a part of the
epiphytic community that is in contact with the sediment. Similar high
rank taxa found in this study were described to be specific for other
species of macrophytes (Burke \emph{et al.}, 2011b; Lachnit \emph{et
al.}, 2011; Bengtsson \emph{et al.}, 2017). In contrast to high
taxonomic ranks, a substantial differentiation between host specific
communities was found, which supports the host-specific hypothesis.
Similar host-specificity was observed for different species of
macroalgae and seagrasses (Lachnit \emph{et al.}, 2011; Roth-Schulze
\emph{et al.}, 2016; Ugarelli \emph{et al.}, 2019; Morrissey \emph{et
al.}, 2019). Taken together, at high taxonomic ranks a core set of taxa
could be described that is characteristic for all or many macrophytes,
while at low taxonomic ranks a community specific to host species could
be identified (Egan \emph{et al.}, 2013).

Few studies describing microbial epiphytic communities were encompassing
seasonal shifts (Tujula \emph{et al.}, 2010; Lachnit \emph{et al.},
2011; Michelou \emph{et al.}, 2013). Seasonal changes in the epiphytic
community were substantial as could be observed in the proportion of
OTUs that could be find at every sampling time (\(\leqslant\) 1.0
\si{\percent}). Interestingly, these OTUs were accounting for a high
proportion of sequences (\(\leqslant\) 51.3 \si{\percent}). A very
similar proportion of persistent OTUs and their sequence contribution
was reported in high frequency studies describing seasonal picoplankton
changes (Gilbert \emph{et al.}, 2009, 2012). In comparison to the
seawater community, a lower degree of seasonal shifts was observed for
the surface associated communities. It seems, that microniches on the
surfaces of macrophytes are providing more stable conditions in
comparison to the seawater. At the level of OTUs seasonal changes of
\emph{Cymodocea nodosa} and \emph{Caulerpa cylindracea} associated
communities were identified that could be linked to the growth cycle of
the seagrass and macroalgae (M. Najdek, personal communication).
\emph{Cymodocea nodosa} was characterized by a Spring community during
maximum seagrass proliferation, a Summer community during a biomass
maximum and a Autumn/Winter community during a biomass decay. In
contrast, \emph{Caulerpa cylindracea} started to proliferate in late
Spring and was characterized only by a Summer community during maximal
biomass increase and by a Autumn/Winter/Spring community when the
biomass were at the peak and the settlement started to subsequently
decay. Similar seasonal changes in the epiphytic community was described
also for other macroalgae (Tujula \emph{et al.}, 2010; Lachnit \emph{et
al.}, 2011). The higher temporal stability of \emph{Caulerpa
cylindracea} surface communities in comparison to \emph{Cymodocea
nodosa} could be also observed in the higher proportion of shared
communities between two consecutive sampling points.

\hypertarget{experimental-procedures}{%
\subsection{Experimental Procedures}\label{experimental-procedures}}

@@

@@

\leavevmode\hypertarget{ref-Bengtsson2017}{}%
Bengtsson, M.M., Bühler, A., Brauer, A., Dahlke, S., Schubert, H., and
Blindow, I. (2017) Eelgrass Leaf Surface Microbiomes Are Locally
Variable and Highly Correlated with Epibiotic Eukaryotes.
\emph{Frontiers in Microbiology} \textbf{8}: 1312.

@@

\leavevmode\hypertarget{ref-Borges2015}{}%
Borges, A.V. and Champenois, W. (2015) Seasonal and spatial variability
of dimethylsulfoniopropionate (DMSP) in the Mediterranean seagrass
Posidonia oceanica. \emph{Aquatic Botany} \textbf{125}: 72--79.

@@

\leavevmode\hypertarget{ref-Fahimipour2017}{}%
Fahimipour, A.K., Kardish, M.R., Lang, J.M., Green, J.L., Eisen, J.A.,
and Stachowicz, J.J. (2017) Globalscale structure of the eelgrass
microbiome. \emph{Applied and Environmental Microbiology} \textbf{83}:

\leavevmode\hypertarget{ref-Gilbert2009}{}%
Gilbert, J.A., Field, D., Swift, P., Newbold, L., Oliver, A., Smyth, T.,
et al. (2009) The seasonal structure of microbial communities in the
Western English Channel. \emph{Environmental Microbiology} \textbf{11}:
3132--3139.

\leavevmode\hypertarget{ref-Gilbert2012}{}%
Gilbert, J.A., Steele, J.A., Caporaso, J.G., Steinbrück, L., Reeder, J.,
Temperton, B., et al. (2012) Defining seasonal marine microbial
community dynamics. \emph{The ISME Journal} \textbf{6}: 298--308.

@@

\leavevmode\hypertarget{ref-Michelou2013}{}%
Michelou, V.K., Caporaso, J.G., Knight, R., and Palumbi, S.R. (2013) The
Ecology of Microbial Communities Associated with Macrocystis pyrifera.
\emph{PLoS ONE} \textbf{8}: e67480.

@@

\leavevmode\hypertarget{ref-Rickert2016}{}%
Rickert, E., Wahl, M., Link, H., Richter, H., and Pohnert, G. (2016)
Seasonal variations in surface metabolite composition of fucus
vesiculosus and fucus serratus from the Baltic Sea. \emph{PLoS ONE}
\textbf{11}:

@@

\leavevmode\hypertarget{ref-Salaun2012}{}%
Salaün, S., Barre, S. la, Santos-Goncalvez, M.D., Potin, P., Haras, D.,
and Bazire, A. (2012) Influence of Exudates of the Kelp Laminaria
Digitata on Biofilm Formation of Associated and Exogenous Bacterial
Epiphytes. \emph{Microbial Ecology} \textbf{64}: 359--369.

### 2020-03-04 submission/supplementary.Rmd
Discussion progress.

# Generating the table
kable(metadata_nseq_notus, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=c("Sample ID", "Community Type", "Date", "Season", "No. of Sequences", "No. of OTUs"), caption="Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample.\\label{nseq_notus}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="6em")
```

>>>>

# Generating the table
kable(metadata_nseq_notus, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=c("Sample ID", "Community Type", "Date", "Season", "No. of Sequences", "No. of OTUs"), caption="Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample. No. of Sequences and OTUs was calculated after the exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences.\\label{nseq_notus}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="6em")
```

### 2020-03-04 submission/supplementary.tex
OTU taxonomy file added to .gitignore.
Discussion progress.

\caption{\label{tab:nseq_notus}Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample.\label{nseq_notus}}\\

@@

\caption[]{Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample.\label{nseq_notus} \textit{(continued)}}\\

>>>>

\caption{\label{tab:nseq_notus}Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample. No. of Sequences and OTUs was calculated after the exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences.\label{nseq_notus}}\\

@@

\caption[]{Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample. No. of Sequences and OTUs was calculated after the exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences.\label{nseq_notus} \textit{(continued)}}\\
